A thesis draft

### 2018-11-23 res/sections/08-Background.tex
Finish SFC part

>>>>

\section{Service Function Caining (SFC)}
Another important component we have to talk about is the SFC, defined as a
concept that it collocates logically above the NFVs. As said in~\cite{rfc7665}:
\begin{displayquote}
The definition and instantiation of an ordered set of service functions and
subsequent ``steering'' of traffic through them is termed Service Function
Chaining (SFC).
\end{displayquote}

\paragraph*{Service Function}
A single element of an SFC is called Service Function (SF), and its duty is to
elaborate the packets incoming and to forward them to the next receiver. SFs, as
for NFs, can be virtualized or be a set of hardware functions. SF does not
necessary know its part of a chain, and this defines it as SFC unaware or, on
the contrary, SFC aware.

\paragraph*{Architectural view}
About the architectural view of SFCs, proposal defines several assumptions on
them, starting from considering every element of the chain an opaque processing
unit. Another important assumpion is that there is no global or standard SF
chaining logic~\cite{rfc7665}. SFC can be easily seen as a graph, because some
SF can have multiple address to forward the elaborated data, thus creating what
is defined as \emph{fork} that ends up forming differen branchs. This coulds
leeds to loops, that must be treated consequently.

\paragraph*{Forwarding strategies}
At high level, SFC proposes an abstracted view of a service, with a defined set
of required SFs that must be executed in a particular order. These services can
be unidirectional if they support data coming only from one direction, thus
following the chain from the first SF to the last one, or they can be
bidirectional, when they supports data coming from both directions, and thus the
first SF can be the last one~\cite{rfc7665}. The forwarding logic has to be
managed by the Service Function Forwarder (SFF), that forwards the data
following the Service Function Path (SFP) defined.

\paragraph*{Data encapsulation}
The data passing inside an SFC must be encapsulated to ensure its integrity.
Data encapsulation enables the possibility of sharing metadata/content, and to
share information about the SFP to follow. Data gets continuously encapsulated
and decapsulated between SFs, to give them the possibility to elaborate the
payload contained.

\subparagraph*{Network Serivce Header (NSH)}
The encapsulation has an header that is well defined and descripted in detail
in~\cite{rfc8300}. This header is composed by a 4-byte base header, and a 4-byte
Service Path Header (SPH). The base header provides information about the services
header and the kind of protocol contained as the payload, while the service path
header provides path identification and location within a define Service Path
(SP). Finally, the Context Header carries metadata.

To further digging in the rabbit hole, the base header has several fields,
identifying the NSH version, the total Time To Live (TTL) of a packet, the
lenght of it, an additional metadata field and at the end it has a field to
identify the protocol of the encapsulated data.

The SPH contains, more than the 24-bit Service Path Identifier (SPI), a Service
Index (SI), that provides the location within the SFP.

\subparagraph*{Context header}
There are two kind of context header definition: one with a fixed context header
length (16-Byte) and one with a dynamic context header length.

\noindent Regarding this field, the standard does not make any assuption about
the content, and it is left free to be filled with custom metadata. The only
requirement is to set this filed with zero when is not used.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.6]{nshtype1}
  \caption[NSH MD Type \texttt{0x1}]{NSH MD Type \texttt{0x1}~\cite{rfc8300}.
    The context header in this NSH has a fixed length. There is another possible
    context header that has a variable length.}
  \label{chap:background:img:nshtype1}
\end{figure}
